Does being on the podium affect Formula 1 drivers' performance in the next race?

### 2025-02-28 inst/eurovision.Rmd
further work on issue #244

for(i in seq_len(ncol(preference))){   # cycle through the rows; each row is a voter
    d <- preference[,i,drop=TRUE]
	eurovision <- eurovision + ordervec2supp(d[!is.na(d)])
} # i loop closes
```

>>>>

for(i in seq_len(ncol(preference))){   # cycle through the rows; each row is a voter
    d <- preference[,i,drop=TRUE]
	eurovision <- eurovision + suppfun(d[!is.na(d)])
} # i loop closes
```

### 2025-02-28 inst/podium.Rmd
further work on issue #244

     o <- fmat[1, , drop = TRUE]
     o[o > 0] <- rank(o[o > 0])
     out <- as.hyper3(ordervec2supp(o))
     for (i in seq(from=2,to=nrow(fmat))){
       if(print){cat(paste(i,"/",nrow(fmat),"\n"))}
       yesterday <- fmat[i-1, , drop = TRUE]
       yesterday[yesterday > 0] <- rank(yesterday[yesterday > 0])  # 'incomplete' functionality of ordertable2supp()
       podium_yesterday <- names(which((yesterday <= 3) & (yesterday>0)))
       d <- fmat[i, , drop = TRUE] # today
       d[d > 0] <- rank(d[d > 0])  # This is the 'incomplete' functionality of ordertable2supp()
       ## Following lines lifted from ordervec2supp()
       nd <- names(d)
       while (any(d > 0)) {
         eligible <- which(d >= 0)
         winner <- nd[d == 1]  # that is, the winner of those still racing
         if(winner %in% podium_yesterday){
           jj <- lambda
         } else {
           jj <- 1
         }
         names(jj) <- winner
         out[jj] %<>% inc    # numerator

>>>>

     o <- fmat[1, , drop = TRUE]
     o[o > 0] <- rank(o[o > 0])
     out <- as.hyper3(suppfun(o))
     for (i in seq(from=2,to=nrow(fmat))){
       if(print){cat(paste(i,"/",nrow(fmat),"\n"))}
       yesterday <- fmat[i-1, , drop = TRUE]
       yesterday[yesterday > 0] <- rank(yesterday[yesterday > 0])  # 'incomplete' functionality of ordertable2supp()
       podium_yesterday <- names(which((yesterday <= 3) & (yesterday>0)))
       d <- fmat[i, , drop = TRUE] # today
       d[d > 0] <- rank(d[d > 0])  # This is the 'incomplete' functionality of ordertable2supp()
       ## Following lines lifted from ordervec2supp()
       nd <- names(d)
       while (any(d > 0)) {
         eligible <- which(d >= 0)
         winner <- nd[d == 1]  # that is, the winner of those still racing
         if(winner %in% podium_yesterday){
           jj <- lambda
         } else {
           jj <- 1
         }
         names(jj) <- winner
         out[jj] %<>% inc    # numerator
